---
title: "Breast cancer prediction"
subtitle: "Shiny Application and Reproducible Pitch"
author: "huangwenxuan"
date: "3/21/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

Breast Cancer is quite common, but if diagnosed early enough, it can be treated well.
the prognosis of five-year survival rate if 85% (US, UK).

[shinyapps](https://venson.shinyapps.io/Breastcancer/?_ga=2.127263309.1540024655.1616291699-1834144672.1616291699)
The diagnosis of Breast Cancer is the key.

1. For the accuracy of the prediction, we use random forest to build our prediction model.
2. We choose to use use [Breast Cancer Coimbra Data Set](https://archive.ics.uci.edu/ml/datasets/Breast+Cancer+Coimbra) from [UC Irvine Machine Learning Repository](https://archive.ics.uci.edu/ml/index.php) to train .
3. We will split the data set into training and testing subset to train and test the model accuracy.
After training the model, we use the testing data to test the accuracy of the model.

## Meachine Learing

Use `multi_cutpointr` from `cutpointr` to find the most effective predictors.

```{r cars, echo = FALSE, message=FALSE}
options(width = 60)
library(caret)
library(cutpointr)
library(dplyr)
library(e1071)
file_url <- "https://archive.ics.uci.edu/ml/machine-learning-databases/00451/dataR2.csv"
file_path <- "dataR2.csv"
if (!file.exists(file_path)) {
  download.file(file_url, destfile = file_path)
}
  breast <- read.csv(file_path)
set.seed(123123)
in_train <- createDataPartition(y = breast$Classification, p = 0.7, list = FALSE)
training <- breast[in_train, ]
testing <- breast[-in_train,]
auc <- select(multi_cutpointr(data = breast, class = "Classification"), AUC, predictor, acc)
auc[order(auc$AUC, decreasing = TRUE),]
```
we select the top 6 predictor to build the model, Which are Glucose ,Resistin ,HOMA, Insulin, BMI and Age.

## Model Accuracy

```{r}
# random forest model
t_control <- trainControl(method = "repeatedcv", number =5, repeats = 15)
set.seed(345)
rffit <- train(factor(Classification) ~ Glucose + Resistin + HOMA + Insulin + BMI + Age ,data = training, method = "rf",ntrees = 15,  trControl = t_control)
# predict
pred <- predict(rffit, newdata = testing)
# predict
confu <- confusionMatrix(pred, factor(testing$Classification))
confu$overall
```

The Accuracy is `r round(confu$overall[1],4)` , the p-Value is `r round(confu$overall[6],7)`, Which is totally acceptable.
That means the result of the prediction is trustworthy.



## Recommedation

1. If the prediction is "Healthy", Congratulations on you. We sill recommend you to live a health life.
eat clean ,do some work out ,keep health.

2. If the prediction is "Patient", We highly recommend you to consult your doctor as soon as possible.
The prediction is not 100% accuracy. standard examine must be take to make a confirmed diagnosis.


